Recent demography drives changes in linked selection across the maize genome

### 2015-11-10 manuscript.tex
updates

We further made use of a large genotyping data set of more than 4,000 maize landraces \cite{Hearne2015} to estimate the modern maize $N_e$ from singleton counts. \jri{imputed or nonimputed?}
We filtered these data to include only SNPs with data in $\geq 1,500$ individuals, and then projected the SFS down to a sample of 500 individuals by sampling each marker without replacement 1,000 times according to the observed allele frequencies.
We then estimated $N_e$ from the data assuming $\mu = 3 \times 10^{-8}$ \cite{clark2005} and the relation  $4N_e\mu = \frac{S}{L}$ \cite{fu1993}, where where $S$ is the total number of singleton SNPs and $L$ is the total number of SNPs in the dataset.

>>>>

We further made use of a large genotyping data set of more than 4,000 partially imputed maize landraces \cite{Hearne2015} to estimate the modern maize $N_e$ from singleton counts. 
We filtered these data to include only SNPs with data in $\geq 1,500$ individuals, and then projected the SFS down to a sample of 500 individuals by sampling each marker without replacement 1,000 times according to the observed allele frequencies.
We then estimated $N_e$ from the data assuming $\mu = 3 \times 10^{-8}$ \cite{clark2005} and the relation  $4N_e\mu = \frac{S}{L}$ \cite{fu1993}, where where $S$ is the total number of singleton SNPs and $L$ is the total number of SNPs in the dataset.
